\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{multicol}

\def\name{Miguel Cardoso Oliveira}

\def\footerlink{https://miguelcfoliveira.github.io/CV/CV.pdf}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Corporate Finance, Financial Distress, Household Finance},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}


\pagestyle{myheadings}
\thispagestyle{empty}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\large}


\setlength\parindent{0em}

% Make lists without bullets
\newenvironment{itemize*}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{https://www.novasbe.unl.pt/en/}{Nova School of Business and Economics} \\
  Campus de Carcavelos, Rua da Holanda, n.º 1 \\ 
  2775-405 Carcavelos, Portugal \\
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +351 969 830 905 \\
    Email: & \href{mailto:miguel.oliveira@novasbe.pt}{\tt miguel.oliveira@novasbe.pt} \\
    Homepage: & \href{https://miguelcfoliveira.github.io}{\tt https://miguelcfoliveira.github.io} \\
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize*}
\item \textbf{Ph.D., Economics \& Finance}, Nova School of Business and Economics \hfill 2019 - 2023
\item \phantom{aaa} Visiting Ph.D. Student at Carnegie Mellon University (Spring 2023)
\item \textbf{Summer School in Structural Estimation} (Corporate Finance), Mitsui Center \hfill August 2021
\item \textbf{M.Sc., Finance}, Nova School of Business and Economics \hfill 2014 - 2016
\item \textbf{B.Sc., Economics}, Nova School of Business and Economics \hfill  2011 - 2014
\item \phantom{aaa} Erasmus Program at Luiss Guido Carli
\end{itemize*}

\section*{Research Interests}
\begin{itemize*}
\item Microeconomics, Corporate Finance, Financial Distress \& Bankruptcy, Household Finance, Macrofinance
\end{itemize*}


\section*{Work in Progress}

\begin{itemize*}
\item \textbf{How costly is default around the world? Evidence from structural estimation}

\medskip

\item \textbf{How Do Households React to Forbearance? Evidence from Transaction-Level Data}

	(with Manuel Adelino and Miguel Ferreira)
\medskip
	
\item \textbf{Do Specialized Distress Investors Undermine Upstream Lending?}

	(with Fernando Anjos and Irem Demirci)

\end{itemize*}

\section*{Teaching Experience}

\begin{itemize*} 
\item \textbf{Nova School of Business and Economics}, Teaching Assistant
\begin{itemize*}
\item Corporate Finance (M.Sc. in Finance) \hfill Fall 2022
\item Data Analytics for Finance (M.Sc. in Finance) \hfill Spring 2022
\item Small Business Management (M.Sc. in Management)  \hfill Fall 2021
\item Small Business Management (M.Sc. in Management)  \hfill Fall 2020
\item International Taxation (M.Sc. in Finance) \hfill Spring 2019
\item Principles of Management (B.Sc. in Economics/Management) \hfill 2016-present
\end{itemize*}
\end{itemize*}

\section*{Academic Honors and Grants}

\begin{itemize*}
\item Ph.D. Scholarship, FCT (\textit{Fundação para a Ciência e Tecnologia}) \hfill 2019 - 2023
\item NOVA SBE Scholarship for merit (M.Sc. partial tuition waiver) \hfill 2014 - 2016
\end{itemize*}

\section*{Service}
\begin{itemize*}
\item Nova Finance Knowledge Center (Member) \hfill 2021-present
\item Nova SBE Planning and Academic Progress Office - Process and Software Development \hfill 2020-present
\end{itemize*}

\section*{Seminars and Conference Presentations}
\begin{itemize*}
\item "Do Specialized Distress Investors Undermine Upstream Lending?"
\begin{itemize}
\item Cambridge Judge Business School - Nova SBE Workshop,  Cambridge 2022 (by co-author)
\end{itemize}
\end{itemize*}

\section*{Discussions}
\begin{itemize*}
\item Cambridge Judge Business School - Nova SBE Workshop,  Cambridge 2022
\item Nova SBE Finance PhD Final Countdown, Lisbon 2022
\item Nova SBE Finance PhD Pitch Perfect, Lisbon 2022
\end{itemize*}

\section*{Non-Academic Experience}

\begin{itemize*}
\item \textbf{Financial Consultant}, Reorganizations \& Bankruptcies w/ small Law firm \hfill 2016-2019
\item \textbf{Founder and Manager}, First Equity, Lda. (Commercial Real Estate) \hfill 2016-2019
\end{itemize*}

\section*{References}
\begin{multicols}{2}
\textbf{Fernando Anjos} \\
Associate Professor of Finance \\
Nova School of Business \& Economics \\
Campus de Carcavelos \\
Rua da Holanda No. 1 \\ 
2775-405 Carcavelos, Portugal \\ 
Email: \href{mailto:fernando.anjos@novasbe.pt}{\tt fernando.anjos@novasbe.pt} 
\columnbreak \hfill

\textbf{Bernardo Melo Pimentel} \\
Head of Economics | Teaching \& Learning Coord. \\
Forward College \\
Rua das Flores 71 \\
1200-193 Lisboa, Portugal \\
Email: \\ 
\href{mailto:bernardo.demelopimentel@forward-college.eu}{\tt bernardo.demelopimentel@forward-college.eu} 
\end{multicols}


\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{Link to latest version}}
  \end{footnotesize}
\end{center}

\end{document}
